A Horrocks-type theorem for even orthogonal $K_2$

### 2020-04-18 dl-paper.tex
Minor fix

Recall from p.~189 of~\cite{Ba74} that there is an exact sequence
\begin{equation} \label{eq:Bass-ES} \xymatrix{1 \ar[r] & \mu_2(R) \ar[r] & \widetilde{P}_n(R) \ar[r] & P_n(R) \ar[r] & 1,}
\end{equation}
in which the group $\mu_2(R) = \{ a \in R^\times \mid a^2 = 1 \}$ is a central subgroup of $\widetilde{P}_n(R)$.
Now by~\cite[\S~7(v)]{Ste67} the group $\KO_2(2n, R) = \Ker(S_n \to G_n)$ is also central in $S_n$.
Thus, we see that $S_n$ is a universal central extension of both $P_n$ and $\widetilde{P}_n$ for $n\geq 5$.

@@

Notice that for $n\geq 3$ the groups $\KO_2(2n, R)$ and $\K_2(\rD_n, R)$ are related via the exact sequence
\[ \xymatrix{ 1 \ar[r] & \K_2(\rD_n, R) \ar[r] & \KO_2(2n, R) \ar[r] & \mu_2(R) \ar[r] & 1,} \]
which follows from~\eqref{eq:Bass-ES} via the snake lemma  (cf. also with~\cite[Corollary~4.3.5]{Ba74}).
On the other hand, from~\cref{lem:lowerKgroups} it follows that $\KO_3(2n, R) \cong \mathrm{K}_3^{\widetilde{G}_n, \widetilde{P}_n}$.

>>>>

Recall from p.~189 of~\cite{Ba74} that for $n\geq 3$ there is an exact sequence
\begin{equation} \label{eq:Bass-ES} \xymatrix{1 \ar[r] & \mu_2(R) \ar[r] & \widetilde{P}_n(R) \ar[r] & P_n(R) \ar[r] & 1,}
\end{equation}
in which the group $\mu_2(R) = \{ a \in R^\times \mid a^2 = 1 \}$ is a central subgroup of $\widetilde{P}_n(R)$.
Now by~\cite[\S~7(v)]{Ste67} the group $\KO_2(2n, R) = \Ker(S_n \to G_n)$ is also central in $S_n$.
Thus, we see that $S_n$ is a universal central extension of both $P_n$ and $\widetilde{P}_n$ for $n\geq 5$.

@@

Notice that the groups $\KO_2(2n, R)$ and $\K_2(\rD_n, R)$ are related via the exact sequence
\[ \xymatrix{ 1 \ar[r] & \K_2(\rD_n, R) \ar[r] & \KO_2(2n, R) \ar[r] & \mu_2(R) \ar[r] & 1,} \]
which is obtained from~\eqref{eq:Bass-ES} and the snake lemma (cf. also with~\cite[Corollary~4.3.5]{Ba74}).
On the other hand, from~\cref{lem:lowerKgroups} it follows that $\KO_3(2n, R) \cong \mathrm{K}_3^{\widetilde{G}_n, \widetilde{P}_n}$.
